Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-09 paper/disc20clustering.tex
refining the model section: Learning model (1)
<= 6

\noindent
\textbf{Learning model.}
We study a variant of Online Balanced Partitioning,
where the communication pattern is \emph{static}:
an adversary determines the pairs of nodes that ever communicate, a priori,
and requests to these pairs arrive indefinitely.
Any algorithm must eventually collocate  pairs of communicating nodes,
as otherwise it cannot be competitive.
As in Henzinger et al. \cite{sigmetrics19_partitioning}, we assume that the communication graph admits a \emph{perfect partition},
i.e., a partition in which no inter-cluster request ever occurs.
%any algorithm must learn this perfect partition.
The algorithm's objective is to \emph{learn} the (static) communication graph on-the-fly,
without executing too many migrations.
For the learning model, we  assume that the migration cost is $\alpha=1$.

@@

\begin{align*}
	\mathit{ALG} (\sigma)	/
	\mathit{OPT} (\sigma)
	\leq
	2\Big(
	\sum_{ t \in T} 3\alpha +
	\sum_{\{u,v\}} C^{m}_{\{u,v\}}
	\Big)	 \big /
	\Big(
	\sum_{ t \in T} \alpha  
	+ \sum_{\{u,v\}} C^{m}_{\{u,v\}}  
	\Big)	< 6.
\end{align*}
%	The claim follows from here.

@@

While we have described our algorithms globally so far, we note that these allow for efficient distributed implementations. 
The algorithm PPL from Section~\ref{sec:ppl} can be distributed
similarly to the approach in~\cite{sigmetrics19_partitioning}.
The algorithm for $k=2$ from Section~\ref{sec:k2} performs only local communication for each request: counters are kept on the clusters and updated locally, and each migration concerns only two clusters.
\medskip
Now, we propose the distributed implementation of the algorithm for $k=3$ from Section~\ref{sec:k3}.
The algorithm performs two non-local operations:
\begin{enumerate}
	\item Broadcasting the end of the phase.\label{it:broadcast}
	\item Component merge.
	\label{it:merge}
\end{enumerate}

>>>>

\noindent
\textbf{Learning model.}
We study a variant of Online Balanced Partitioning,
where the communication pattern is \emph{static}:
an adversary determines the pairs of nodes that ever communicate, a priori,
and requests to these pairs arrive indefinitely.
Any algorithm must eventually collocate  pairs of communicating nodes,
as otherwise it cannot be competitive.
As in Henzinger et al. \cite{sigmetrics19_partitioning}, we assume that the communication graph admits a \emph{perfect partition},
i.e., a partition in which no inter-cluster request ever occurs.
%any algorithm must learn this perfect partition.
The algorithm's objective is to \emph{learn} the (static) communication graph
 while serving all requests,
and without executing too many migrations.
For the learning model, we  assume that the migration cost is $\alpha=1$.

@@

\begin{align*}
	\mathit{ALG} (\sigma)	/
	\mathit{OPT} (\sigma)
	\leq
	2\Big(
	\sum_{ t \in T} 3\alpha +
	\sum_{\{u,v\}} C^{m}_{\{u,v\}}
	\Big)	 \big /
	\Big(
	\sum_{ t \in T} \alpha  
	+ \sum_{\{u,v\}} C^{m}_{\{u,v\}}  
	\Big)	\leq 6.
\end{align*}
%	The claim follows from here.

@@

\mahmoud{mention the offline approx.}
While we have described our algorithms globally so far, we note that these allow for efficient distributed implementations. 
The algorithm PPL from Section~\ref{sec:ppl} can be distributed
similarly to the approach in~\cite{sigmetrics19_partitioning}.
The algorithm for $k=2$ from Section~\ref{sec:k2} performs only local communication for each request: counters are kept on the clusters and updated locally, and each migration concerns only two clusters.
\medskip
Now, we propose the distributed implementation of the algorithm for $k=3$ from Section~\ref{sec:k3}.
The algorithm performs two non-local operations:
\begin{enumerate}
	\item Broadcasting the end of the phase.\label{it:broadcast}
	\item Component merge.
	\label{it:merge}
\end{enumerate}
